Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-03-09 FrontMatter/Abstract.tex
front matter finalized

This dissertation consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WS2}-\ce{WO3}, respectively. Systematical investigation of the \ce{WO3} nanostructure prepared by the CVD method with tungsten powders as precursor led to the following accomplishments:
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item the discovery of \ce{Na5W14O44} nanowires;
\item a knowledge of the delicate role of sodium in tungsten source powders; and
\item a seeded growth method to produce high quality \ce{WO3} nanowires.
\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended the vapor-liquid-solid strategy into \ce{MoO3} 1D nanostructure growth and discovered two morphologies of \ce{MoO3}: ultra-longbelts and microtowers. Careful observation in extensive experiments identified the catalytic role of sodium hydroxide during the growth of \ce{MoO3} and readily proved that the catalytic behavior also exists with other alkali-based metal contents. The third part of this work moved the investigation center from growth to property characterization. A novel TEM-Raman integrated study was performed on \ce{WS2}-\ce{WO3} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman spectroscopy, and photoluminescence spectroscopy on individual nanowires. The single-walled \ce{WS2} tubular nanostructure was first identified. The combined results further illustrated the existence of \ce{WS2} wall number dependent Raman fingerprints on resonant Raman spectra.

>>>>

This dissertation consists of three main parts, each centering on \ce{WO3}, \ce{MoO3}, and \ce{WO3}-\ce{WS2}, respectively. Systematical investigation of the \ce{WO3} nanostructure prepared by the CVD method with tungsten powders as precursor led to the following accomplishments:
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item the discovery of \ce{Na5W14O44} nanowires (NWs);
\item a knowledge of the delicate role of sodium in tungsten source powders; and
\item a seeded growth method to produce high quality \ce{WO3} NWs.
\end{enumerate*} Enlightened by the intricate interactions between sodium content and tungsten oxide, this dissertation extended the vapor-liquid-solid strategy in to \ce{MoO3} 1D nanostructure growth and discovered two morphologies of \ce{MoO3}: long nano-belts and micro-towers. Careful observation in extensive experiments identified the catalytic role of sodium hydroxide during the growth of \ce{MoO3} and readily proved that the catalytic behavior also exists with other alkali metal compounds. The third part of this work moved the investigation center from growth to structure and property characterization. A novel integrated structure-property (transmission electron microscopy-Raman spectroscopy, TEM-Raman) study was performed on \ce{WO3}-\ce{WS2} core-shell NWs, allowing for the observation of high resolution TEM imaging, Raman spectroscopy, and photoluminescence spectroscopy on individual nanowires. The TEM-Raman combined results further illustrated that the profiles of resonant Raman spectra exhibit strong dependence on the wall number of \ce{WS2}. This Raman fingerprints can provide a rapid approach for the optical identification of few-walled \ce{WS2} tubular structures.

### 2015-03-09 FrontMatter/FrontMatter.tex
front matter finalized

\begin{ackn}
Studying in UNC Charlotte has been an unique and rewarding experience for myself, which I shall recall frequently for a long time to come. So I am grateful to all the people here I have spent time with. Dr. Haitao Zhang has been an excellent advisor to me. I enjoyed the time learning a new set of skills, discussing research questions, and obtaining important life lessons from him. I thank Dr. Davies for the help she gave when I joined the Optical Science and Engineering program; I thank Dr. Terry Xu for allowing me to work in her lab since 2012, within which I finished most of the crystal growth work. I also thank Dr. Yong Zhang for the access to Raman instrument in his group, without which my research would be seriously diminished. I appreciate the financial supports of GASP in UNC Charlotte, the research assistantship from National Science Foundation (DMR-1006547), and the teaching assistantship from Physics and Optical Science department. I also appreciate the Center for Optoelectronics and Optical Communications at UNC Charlotte for the support in multiuser facilities. I would also like to thank all my friends and/or research partners I have met in Charlotte: Dr. Bob Cao, Dr. Jianwei Wang, Liqin Su, Henan Liu, Jinghua Ge, Siang Yee Chang, Zhe Guan, and Youfei Jiang.

@@

\begin{flushright}

\emph{Sheng, Tao}

\emph{January 2015}

\emph{Charlotte, NC}

>>>>

\begin{ackn}
Studying in UNC Charlotte has been an unique and rewarding experience for myself, which I shall recall frequently for a long time to come. So I am grateful to all the people here I have spent time with. Dr. Haitao Zhang has been an excellent advisor to me. I enjoyed the time learning a new set of skills, discussing research questions, and obtaining important life lessons from him. I thank Dr. Davies for the help she gave when I joined the Optical Science and Engineering program; I thank Dr. Terry Xu for allowing me to work in her lab since 2012, within which I finished most of the crystal growth work. I also thank Dr. Yong Zhang for the access to Raman instrument in his group, without which my research would be seriously diminished. I appreciate the financial supports of GASP in UNC Charlotte, the research assistantship from National Science Foundation (DMR-1006547), and the teaching assistantship from Physics and Optical Science department. I also appreciate the Department of Mechanical Engineering and Engineering Science and the Center for Optoelectronics and Optical Communications at UNC Charlotte for supports in multiuser facilities. I would also like to thank all my friends and/or research partners I have met in Charlotte: Dr. Bob Cao, Dr. Jianwei Wang, Liqin Su, Henan Liu, Jinghua Ge, Siang Yee Chang, Zhe Guan, and Youfei Jiang.

@@

\begin{flushright}
\vspace{2in}
\emph{Sheng, Tao}

January 2015

Charlotte, NC
